---
title: "workout01"
output: github_document
---

## Rankings of Teams
```{r}
#input the nba2018-teams.csv file into the Rmd file, and pull up ggplot and dplyr
library(tidyverse)
teams <- read_csv('~/Desktop/stat133/workout/workout1/data/nba2018-teams.csv')
```

### Basic Rankings
```{r graph-salary}
#graph teams on horizontal bar chart ranked by total salary, with an average team salary line
ggplot(teams, aes(x = reorder(team, salary), y = salary)) +
  labs(x = 'team') +
  geom_bar(stat = 'identity') +
  coord_flip() +
  geom_hline(aes(yintercept = mean(salary)), color = "Red")
```
```{r graph-points}
#graph teams on horizontal bar chart ranked by total points, with an average team points line
ggplot(teams, aes(x = reorder(team, points), y = points)) +
  labs(x = 'team') +
  geom_bar(stat = 'identity') +
  coord_flip() +
  geom_hline(aes(yintercept = mean(points)), color = "Red")
```
```{r graph-efficiency}
#graph teams on horizontal bar chart ranked by efficiency, with an average team efficiency line
ggplot(teams, aes(x = reorder(team, efficiency), y = efficiency)) +
  labs(x = 'team') +
  geom_bar(stat = 'identity') +
  coord_flip() +
  geom_hline(aes(yintercept = mean(efficiency)), color = "Red")
```

### Rationale behind my index
* create index which is (salary divided by average salary) + (efficiency divied by average efficiency)
* this index shows how teams compare to the average in both salary and efficiency
* salary and efficiency are both key, because they show what a team can afford as far as players, and efficiency sums up all of the in game statistics that show how well teams perform
* the reason I take the average is to make so both salary and efficiency are scaled evenly
* by doing this, the average will be exactly centered at 2

### Graph with My Index
```{r graph-with-my-index}
#add my index to teams
teams <- mutate(teams, index = (salary / mean(salary)) + (efficiency / mean(efficiency)))

#graph teams on horizontal bar chart ranked by my index, with an average of these indexes drawn vertically
ggplot(teams, aes(x = reorder(team, index), y = index)) +
  labs(x = 'team') +
  geom_bar(stat = 'identity') +
  coord_flip() +
  geom_hline(aes(yintercept = mean(index)), color = "Red")
```

### Comments and Reflections
* This was my first time doing something like this, and I thought it was a cool project, but I got stuck on parts and that was quite frustrating
* It was also my first time using relative paths, and I found them to be extremely helpful
* It was my first time using R script, which I found to be pretty straightforward
* The hardest thing for me was figuring out how to break the data from nba2018.csv into teams, even though we did similar things in lab
* I thought everything we hadn't explicitly done in lab/hw was pretty self-explanatory
* A classmate helped me understand the best way to compile the data
* It took me around 7 hours to finish this project, considering I got stuck quite a few times and had to work through some problems
* Figuring out how to make nba2018-teams.csv was the most time consuming part of this project for me
* I thought the last question was the most interesting, as it made us think critically about what is the best way to rank teams as a whole
